Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm

### 2024-08-16 paper/main.tex
Added a TikZ picture of the structure of the receiver

\usepackage{tikz}
\usetikzlibrary{calc,patterns,patterns.meta}

@@

\section{Principle of a DCF77 receiver}
\begin{figure*}[!htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{
        \begin{tikzpicture}
            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size

@@

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\usepackage{tikz}
\usetikzlibrary{calc, patterns, patterns.meta, shapes.geometric, arrows.meta, positioning, fit}

@@

\section{Principle of the receiver}
To understand the principle of the receiver, it is compared to the common structure that is used in radio controlled clocks.
\begin{figure}[htbp]
    \centering
    \resizebox{0.48\textwidth}{!}{
        \begin{tikzpicture}
            % Block styles
            \tikzstyle{block} = [rectangle, draw, text width=4.5em, text centered, minimum width=6em, minimum height=4em]
            \tikzstyle{block_dashed} = [rectangle, draw, text width=2em, text centered, minimum width=4em, minimum height=4em, dashed]
            % Input and output
            \begin{scope}[shift={(-3,0)}] % Adjust the position of the antenna
                \coordinate (antenna) at (0,0);
                \draw[thick] (0,0) -- (0,1); % Antenna pole
                \draw[thick] (-0.25,1) -- (0,0.75); % Antenna horizontal line
                \draw[thick] (0.25,1) -- (0,0.75); % Antenna horizontal line
            \end{scope}
            \node[block, right=of antenna, minimum width=4em, minimum height=4em] (bpf) {BPF};
            \node[block, right=of bpf] (rfamp) {RF Amp};
            \node[block, right=of rfamp] (adc) {ADC};
            \node[block, below=of adc] (timer) {Timer};
            \node[block, right=of adc] (goertzel) {Goertzel Algorithm};
            \node[block, right=of goertzel] (det) {Detector};
            % Connections
            \draw[thick] (antenna) -- (bpf);
            \draw[->] (bpf) -- (rfamp); % Connection from antenna to RF amplifier
            \draw[->] (rfamp) -- (adc);
            \draw[->] (timer) -- (adc);
            \draw[->] (adc) -- (goertzel);
            \draw[->] (goertzel) -- (det);

            \node[draw, dashed, fit={(antenna) (bpf)}, inner sep=12pt] (tank_circuit) {};
            \node[below=0.5em of tank_circuit, align=center] {Tuned Tank Circuit};
        \end{tikzpicture}
    }
\end{figure}
\FloatBarrier\noindent
Test

\begin{figure*}[!htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{
        \begin{tikzpicture}
            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size

@@
